Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
bergerud1989 ref
P5

Forage limitation and over-grazing is a major concern for caribou populations:
it can reduce female reproductive success [@Schaefer2016] and thus could lead to
movement between islands. Forage scarcity has been proposed as a potential
reason for caribou moving between arctic islands on the sea-ice in winter
[@Miller1977].

>>>>

Forage limitation and over-grazing is a major concern for caribou populations
and can lead to reduced female reproductive success [@Schaefer2016]. Forage
scarcity has been proposed as a potential reason for caribou moving between
arctic islands on the sea-ice in winter [@Miller1977]. For the Fogo Island
population, as the population grew and predation pressure was insufficient to
maintain population density, forage depletion could lead caribou to make
similar, but riskier and more costly, movements between islands during the
ice-free season. Given the small size of other islands near Fogo, over-grazing
by newly arrived caribou could rapidly deplete forage on an annual cycle
[@Bergerud1990], leading to more frequent movements back and forth between
islands rather than permanent relocation.
